|

### 2022-11-04 manuscript.Rmd
add more bib library

bibliography: ["bib/references.bib", "bib/packages.bib"]
csl: "bib/chicago-author-date.csl"
output:
  rticles::jds_article: 
    citation_package: default
    includes:
      in_header: header.tex #header-hidden.tex can be used when creating an anonymized version for review
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
    citation_package: default
---

>>>>

bibliography: ["bib/references.bib", "bib/packages.bib", "bib/teachinga11y.bib"]
csl: "bib/chicago-author-date.csl"
output:
  rticles::jds_article: 
    citation_package: default
    includes:
      in_header: header.tex #header-hidden.tex can be used when creating an anonymized version for review
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
    citation_package: default
---
